Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Standardize to "cover cluster"

A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
reef characteristics that influence its temporal behaviour, and thus its cluster assignment
into Low, Medium, or High. Reef median depth, carrying capacity and mean time series DHW
level have the highest feature importance scores, accounting for 29%, 15% and 15% predictive
importance respectively (@fig-ts-cluster-pdp; Panel A). Reef weighted incoming connectivity,
outgoing connectivity strength, source-to-sink connectivity ratio and larval retention
probability account for \~12%, 11%, 10% and 8% respectively.

>>>>

A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
reef characteristics that influence its temporal behaviour, and thus its assignment into
Low, Medium, or High cover clusters. Reef median depth, carrying capacity and mean time
series DHW level have the highest feature importance scores, accounting for 29%, 15% and 15%
predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Area weighted incoming
connectivity, outgoing connectivity strength, source-to-sink connectivity ratio and larval
retention probability account for \~12%, 11%, 10% and 8% respectively.
